Unfolding the City: \wq{Exploring Urban Spatial Attractiveness with Individual Characteristics}

### 2019-04-22 manuscript/template.tex
at first, read readme.txt in manuscript folder

\usepackage{url}
\usepackage{ulem}

\usepackage{color, xcolor}
\definecolor{darkg}{rgb}{0,0.6,0}
\definecolor{lgreen}{rgb}{0,0.8,0}
\definecolor{purple}{rgb}{0.93,0.48,0.03}
\definecolor{orange}{rgb}{0.43,0.48,0.03}
% \ifdraft
%Our comments:
\newcommand{\lmc}[1]{{\color{lgreen}[LM: #1]}}
\newcommand{\wqc}[1]{{\color{orange}[WQ: #1]}}

%Noticable new adds:
\newcommand{\wq}[1]{{\color{blue}#1}}
\newcommand{\lm}[1]{{\color{darkg}#1}}

@@

\usepackage{algpseudocode}
\usepackage{natbib}
\usepackage[misc]{ifsym}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Unfolding the City: \wq{Exploring Urban Spatial Attractiveness with Social Characteristics}}
%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}

@@

\section{Introduction}
\label{intro}
\wqc{change mobility pattern to spatial attractiveness}
The science fiction \textit{Folding Beijing}~\citep{hao2016_foldingbeijing} depicts a world where three classes of people live in independent spatial-temporal patterns, though sharing the same earth surface. This is an artistical metaphor for one potential fact that people make different decisions in visiting places according to individual determinants, such as social, economic, educational factors, etc. This phenomenon has attracted the research interest for a long time in the sociological field. Back to 1970, Pahl~\citep{pahl1975whose} posed the question `whose city` and interest in understanding the territorial inequalities. Contemporary contestation also continually raise the banner `The City Belongs to All!'~\citep{Mayer2017_whosecity}. Having a good understanding of how the mobility patterns relate to characterized individuals sheds light on region utilization, diversity mix-up, and opportunities promotion.

@@

\wqc{Common human mobility indicators: travel distance, travel time, travel frequency, radius of gyration and movement entropy. }\\
\wq{Spatial attractiveness is an important concept in GIS. Explain why. To derive the details, we interview the expert in GIS. Some questions like, how citizens live in the city, where they live, work and entertain? Which place is popular? For different citizens, whether a place has the same attraction? ... With these questions, we summarize them into the tasks below, which need to be answered by our system.}

\sout{The design of the system is driven by tasks, to align the analysis of mobility patterns with individual characteristics. Before diving into the design of the system, introduce the couple of specifical tasks the system intended for.}

\begin{itemize}
\item \textit{Task 1: Identify the group with specific individual characteristics}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
\item \textit{Task 2: Explore the mobility patterns of a group}: to explore where, how and why an interested group go in the city.
\item \textit{Task 3: Compare mobility patterns among multiple groups}: to know the similarities and differences between different groups in their mobility patterns, to investigate the relationship between movement and individual characteristics.
\end{itemize}

@@

\section{Visual Design}
\lm{With the design consideration (introduced in Section~\ref{}), we design a visual analytic system...} \lm{Show a overview figure, to introduce the relationship between multiple views}

With those design considerations, we develop a visual analytics system as \wq{Figure~\ref{fig:interfaceDraft} shows.} \wqc{instead of fig. teaser} It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}). In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics. With the chosen group of individuals, its moving related information is visualized and explored in a 2.5D spatio-temporal view.

@@

\paragraph{Star-like Glyph} \lm{To compare over multiple individuals, a star-like glyph is designed to summary each individual, to ease the comparison by common cooridnating configurations....}

@@

@@

\wq{\subsection{XXXX Projection of Individuals}}
\wqc{A octagon radar graph to position all citizens. A clustering algorithm for commend similar persons into a new group.(maybe: interactions to set the weight of each characteristic)}

@@

\subsection{2.5D Spatial Visualization}
\wqc{this part may be deleted.}

\label{subsec:25D}

@@

To compare the mobility patterns across different groups of people, a Small Multiple dock is used to reserve the ever explored interesting result (Figure~\ref{fig:teaser}(f)). To simply the comparison over spatial distribution, the snapshot is also rendered in the 2.5D space, which maintains the same interactions as the main 2.5D space does.

\wq{\subsection{A glyph design details (in view3)}
We design a kind of glyph to express a high-dimensional travel indicators. It will be embeded in the map view\wqc{for case1}.}

\wq{\subsection{Ranking or comparison method (in view4)}
\wqc{for case3}We design ranking/comparison method with different weight of different purpose or different groups.}

@@

\subsection{Case 1: Work-life Balance VS Income/Education}
\wqc{Aim1: use view1 and view2 for groups. Aim2: show their basic activity spaces.}

@@

Before diving into the complex mobility pattern analysis, we explore the home distribution of the four groups. As Figure~\ref{case12} shows, \textit{top aristocracy} and most of \textit{new rich} live concentrated in the downtown area of Shenzhen, where the living cost is higher, especially the housing cost. A small part of \textit{new rich} lives far away from the downtown, maybe because they don't have to work in downtown. The \textit{underclass} distribute more dispersively all over the whole city. Compared to the rich, they prefer the outer space because of the lower living cost. Lots of \textit{antizen} live in Nanshan District, where there are many universities and high-tech industrial parks full of well educated people. \wq{The glyphs on the map means the travel distance(even differentiate home-work distance(which is an important in mobility research), and extended travel distance), travel radius.} \wqc{the 3rd design in Section.design, a kind of glyph for high-dimensional mobility indicator}

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case1_2}
 \caption{Home Distributions of the Four Groups}
 \label{case12}
\end{figure}

\wqc{paragraph below may be deleted. It is about attractiveness entropy, which in case3}
To have a better knowledge of mobility patterns of the four groups, trips are categorized into three categories, ``home", ``work'' for regular trips with the purpose of going home, work (or school for students), ``other'' for irregular trips with the purpose of shopping, visiting friends. Figure~\ref{case13}(a) shows the 2.5D overview of the three kinds of traveling categories. Each TAZ is grown to the same height, i.e., the unit one, and the height proportion of each traveling categories encodes the percentage of certain purpose in the whole, pink for ``others'', blue for ``work'' and green for ``home''. Although inside TAZ prisms are blocked in the Figure~\ref{case13}, our attention is drawn to the lifestyle of \textit{New Rich}. It is founded that the \textit{New Rich} travel for ``other'' purpose a lot, compared to other groups. To explore further, the detail slicing (introduced in Section~\ref{subsec:25D}) is applied to the four groups. Figure~\ref{case13}(b) shows three slices. It can be seen that individuals with low income (\textit{underclass} and \textit{antizen}) spend relatively more time on work, especially the \textit{underclass}. Working percentage is very small in-group \textit{new rich}. They live a more diverse lifestyle because they do many other things (the pink ones) except working.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case1_3}
 \caption{Mobility Patterns of ``work", ``home" and ``not essential" of the Four Groups: (a) the overview of the three pecentage; (b) three slices for detailed comparison.}
 \label{case13}
\end{figure}

\subsection{Case 2: Spatial Attractiveness Based on One Purpose}
\wqc{aim: select one purpose; View3 shows spatial attractiveness, including: quantity, distance, （direction）; View4 shows ranking of origins, (or others); (add a interaction in view5 for citizens in selected grid.)}

\wq{Due to the various functions of the areas, for different space, the attractiveness for different aims differs. Therefore, in this case, we demonstrate the use of the system for exploring the spatial attractiveness for one purpose.}

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case2}
 \caption{Home-work distances of different groups: (a) with different salary levels; (b) with or without house.}
 \label{case2}
\end{figure}

We explore the home-work distance of groups with and without a house.
Figure~\ref{case2}(b) shows the close-up views. It is found that the Nanshan District has a shorter home-work distance for individuals without a house, while Futian District has shorter for those with a house. Nanshan is relatively newer to Futian so that there might be more easily-accessible houses to be rent.

\subsection{Case 3: Spatial Attractiveness Based on Mixed Purposes}
\wqc{aim: with mixed purposes, show attractiveness quantity and entropy. View3 shows spatial attractiveness, including: quantity, distance, （direction）; View4 shows ranking of origins, (or others); (add a interaction in view5 for citizens in selected grid.)}

\wq{Due to the various functions of the areas, for different space, the attractiveness for different aims differs. Therefore, in this case, we demonstrate the use of the system for exploring the spatial attractiveness for one purpose.}

@@

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case3_2}
 \caption{The ``dinner or entertain" purpose of four groups with different jobs}
 \label{case32}
\end{figure}

>>>>

\usepackage{url}

\usepackage{color, xcolor}
\definecolor{darkg}{rgb}{0,0.6,0}
\definecolor{lgreen}{rgb}{0,0.8,0}
\definecolor{purple}{rgb}{0.93,0.48,0.03}
\definecolor{orange}{rgb}{0.43,0.48,0.03}
% \ifdraft
%Our comments:
\newcommand{\lmc}[1]{{\color{lgreen}[LM: #1]}}
\newcommand{\wqc}[1]{{\color{orange}[WQ: #1]}}
\newcommand{\wq}[1]{{\color{blue}#1}}
\newcommand{\lm}[1]{{\color{darkg}#1}}

@@

\usepackage{algpseudocode}
\usepackage{natbib}
\usepackage[misc]{ifsym}

\begin{document}

\title{Unfolding the City: \wq{Exploring Urban Spatial Attractiveness with Individual Characteristics}}
%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}

@@

\section{Introduction}
\iffalse
What is it that makes some places, regions or nations appear more attractive than others to live in, visit or invest in? Does it depend on the particular characteristics or situation of the persons considering the attractiveness, in what phase in life the persons find themselves, or are there some common features, perhaps place characteristics that are viewed positively by all, independently of context?

\fi

\label{intro}
\wqc{change mobility pattern to spatial attractiveness}\\
The science fiction \textit{Folding Beijing}~\citep{hao2016_foldingbeijing} depicts a world where three classes of people live in independent spatial-temporal patterns, though sharing the same earth surface. This is an artistical metaphor for one potential fact that people make different decisions in visiting places according to individual determinants, such as social, economic, educational factors, etc. This phenomenon has attracted the research interest for a long time in the sociological field. Back to 1970, Pahl~\citep{pahl1975whose} posed the question `whose city` and interest in understanding the territorial inequalities. Contemporary contestation also continually raise the banner `The City Belongs to All!'~\citep{Mayer2017_whosecity}. Having a good understanding of how the mobility patterns relate to characterized individuals sheds light on region utilization, diversity mix-up, and opportunities promotion.

@@

A discussion with experts in GIS. We summarize the analytic tasks identified from the interviews of domain experts. Then the workflow of the proposed visual analytics system.

\subsection{Goal}
\wqc{Common human mobility indicators: travel distance, travel time, travel frequency, radius of gyration and movement entropy. }\\

Spatial attractiveness is an important concept to evaluate ... in commercial activity, tourism and urban research. We interview the expert in GIS.  There are some core research concerns derived from domain exports.

\begin{itemize}
  \item \textit{Diversity of spatial attractiveness} Two types of diversity: diversity of the attracted persons, and diversity of attractiveness indicators. \wqc{cannot find this concept in papers, and, i am not sure about ``indicator"}
  \item \textit{Magnitude of spatial attractiveness} How many persons could be attracted and how much the difficulty they overcome. \wqc{there is equation in related paper to support this.}
\end{itemize}
With these questions, we summarize them into the tasks below, which need to be answered by our system.

\subsection{Tasks}
\lm{The exploration of core concepts above are resolved further with following tasks... to align the analysis of mobility patterns with individual characteristics. Before diving into the design of the system, introduce the couple of specifical tasks the system intended for.}

%The design of the system is driven by tasks, to align the analysis of mobility patterns with individual characteristics. Before diving into the design of the system, introduce the couple of specifical tasks the system intended for.

\begin{itemize}
\item \textit{Task 1: Identify the group with specific individual characteristics\wqc{What kind of citizens tend to be attracted?}}: to get groups of people with common or close attributes, to explore the correlation among individual characteristics.
\item \textit{Task 2: Why the attracted citizens are attracted?}: to explore ...
\item \textit{Task 3: How many citizens are extracted?}: to express ...
\item \textit{Task 4: Where do the attracted citizens come from?}: City has different function areas. Some areas meet all the basic requirements of citizens' living activities, while some cannot. ... to know the similarities and differences between different groups in their mobility patterns, to investigate the relationship between movement and individual characteristics.
\end{itemize}

@@

\section{Visual Design}

With those design considerations (introduced in Section~\ref{}), we develop a visual analytics system as Figure~\ref{fig:interfaceDraft} shows. It composes of individual panel (the left part) for individuals (\textit{Task 1}) and spatial panel (the right part) for the mobility pattern (\textit{Task 2 and 3}). In the individual panel, interactive infographics, t-SNE visualization, and data-driven profiles support users to narrow the scope down to groups of individuals with interested characteristics. With the chosen group of individuals, its moving related information is visualized and explored in a 2.5D spatio-temporal view. \lmc{Show a overview figure, to introduce the relationship between multiple views}

@@

\paragraph{Star-like Glyph} \lm{To compare over multiple individuals, a star-like glyph is designed to summary each individual, to ease the comparison by common coordination configurations....}

@@

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/design_profile}
 \caption{Design Profile: the eight characteritical domains are encoded and organized in an organic human figure.}
 \label{fig:design_profile}
\end{figure}

@@

\wq{\subsection{XXXX Projection of Individuals}}
\wqc{A octagon radar graph to position all citizens. A clustering algorithm for commend similar persons into a new group.(maybe: interactions to set the weight of each characteristic)} \lmc{Yes, I think an interactive weight adjustment is good.}

@@

\iffalse
\subsection{2.5D Spatial Visualization}
\label{subsec:25D}

@@

To compare the mobility patterns across different groups of people, a Small Multiple dock is used to reserve the ever explored interesting result (Figure~\ref{fig:teaser}(f)). To simply the comparison over spatial distribution, the snapshot is also rendered in the 2.5D space, which maintains the same interactions as the main 2.5D space does.
\fi

\wq{\subsection{A glyph design to show travel indicator (in view3, in case1)}
We design a kind of glyph to express a high-dimensional travel indicators. It will be embeded in the map view\wqc{for case1}.
The elements may be included in the glyph:
\begin{itemize}
  \item (home-work distance)
  \item travel distance
  \item travel radius
  \item travel frequency
\end{itemize}}

\wq{\subsection{A glyph design to show attractiveness (in view3, in case2)}
We design a kind of glyph to express spatial attractiveness.
The elements may be included in the glyph:
\begin{itemize}
  \item quantity
  \item distance
\end{itemize}}

\wq{\subsection{A glyph design to show attractiveness diversity(in view3, in case3)}
We design a kind of glyph to express spatial attractiveness.
The elements may be included in the glyph:
\begin{itemize}
  \item how many kinds of purpose?
  \item the percentage of each purpose?
\end{itemize}

(if comparison between groups, the glyph up, show the diversity of multiple groups at the same time.)}

@@

\wq{\subsection{Case 1: find diversity of citizens based on social characteristics}}
\wqc{Aim1: use view1 and view2 for groups. Aim2: show their basic activity spaces in view3 and view4. text no changes yet.}

@@

Before diving into the complex mobility pattern analysis, we explore the home distribution of the four groups. As Figure~\ref{case1draft} shows, \textit{top aristocracy} and most of \textit{new rich} live concentrated in the downtown area of Shenzhen, where the living cost is higher, especially the housing cost. A small part of \textit{new rich} lives far away from the downtown, maybe because they don't have to work in downtown. The \textit{underclass} distribute more dispersively all over the whole city. Compared to the rich, they prefer the outer space because of the lower living cost. Lots of \textit{antizen} live in Nanshan District, where there are many universities and high-tech industrial parks full of well educated people.

\wq{The glyphs on the map means the travel distance, travel radius..., which is an important in mobility research. Describe the difference.}\\
\wqc{the 3rd design in Section.design, a kind of glyph for high-dimensional mobility indicator.}

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case1draft}
 \caption{Home Distributions of the Four Groups}
 \label{case1draft}
\end{figure}

\iffalse
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case1_2}
 \caption{Home Distributions of the Four Groups}
 \label{case12}
\end{figure}

To have a better knowledge of mobility patterns of the four groups, trips are categorized into three categories, ``home", ``work'' for regular trips with the purpose of going home, work (or school for students), ``other'' for irregular trips with the purpose of shopping, visiting friends. Figure~\ref{case13}(a) shows the 2.5D overview of the three kinds of traveling categories. Each TAZ is grown to the same height, i.e., the unit one, and the height proportion of each traveling categories encodes the percentage of certain purpose in the whole, pink for ``others'', blue for ``work'' and green for ``home''. Although inside TAZ prisms are blocked in the Figure~\ref{case13}, our attention is drawn to the lifestyle of \textit{New Rich}. It is founded that the \textit{New Rich} travel for ``other'' purpose a lot, compared to other groups. To explore further, the detail slicing (introduced in Section~\ref{subsec:25D}) is applied to the four groups. Figure~\ref{case13}(b) shows three slices. It can be seen that individuals with low income (\textit{underclass} and \textit{antizen}) spend relatively more time on work, especially the \textit{underclass}. Working percentage is very small in-group \textit{new rich}. They live a more diverse lifestyle because they do many other things (the pink ones) except working.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case1_3}
 \caption{Mobility Patterns of ``work", ``home" and ``not essential" of the Four Groups: (a) the overview of the three pecentage; (b) three slices for detailed comparison.}
 \label{case13}
\end{figure}
\fi

\subsection{Case 2: Diversity of spatial attractiveness of indicators}
\wqc{aim: with mixed purposes, show attractiveness quantity and entropy. View3 shows spatial attractiveness, including: quantity, distance, （direction）; View4 shows ranking of origins, (or others); (add a interaction in view5 for citizens in selected grid.)}

\wq{Due to the various functions of the areas, for different space, the attractiveness indicators differs. Therefore, in this case, we demonstrate the use of the system for exploring diversity of spatial attractiveness indicators. }

\wq{As Figure~\ref{case2draft} shows, in view3, glyph represents $\textbf{the quantity}$ and $\textbf{value of mixture of purposes}$. \wqc{(if we decide to give a computing equation to define it.)} in view4, ranking of each grid based on the quantity of each purpose.}
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case2draft}
 \caption{Trip purposes distribution of four groups with different jobs}
 \label{case2draft}
\end{figure}

@@

\iffalse
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case3_2}
 \caption{The ``dinner or entertain" purpose of four groups with different jobs}
 \label{case32}
\end{figure}
\fi

\subsection{Case 3: Magnitude of Spatial Attractiveness}
\wqc{aim: select one purpose to show how many and where and how long. Use View3 and view4.}

\wq{When zooming in to explore with only one purpose, we demonstrate the use of the system for exploring the magnitude of spatial attractiveness.}

\wq{As Figure~\ref{case3draft} shows, in view3, glyph represents $\textbf{the quantity}$ and $\textbf{how many grids are linked(i.e. area)}$ and $\textbf{distribution of distances}$. in view4, show $\textbf{where are the linked grids}$ and $\textbf{the quantity of each linked grid}$ and $\textbf{distance}$. \wqc{not sure the form in view4, map or chart? if map, 1D or 2.5D?}}
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case3draft}
 \caption{Home-work distances of different groups: (a) with different salary levels; (b) with or without house.}
 \label{case3draft}
\end{figure}

\iffalse
\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/case2}
 \caption{Home-work distances of different groups: (a) with different salary levels; (b) with or without house.}
 \label{case2}
\end{figure}

We explore the home-work distance of groups with and without a house.
Figure~\ref{case2}(b) shows the close-up views. It is found that the Nanshan District has a shorter home-work distance for individuals without a house, while Futian District has shorter for those with a house. Nanshan is relatively newer to Futian so that there might be more easily-accessible houses to be rent.
\fi
